%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItemWithoutTitle}[1]{
	\item\small{
		{\vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{{\LARGE Masavir Khliq}} & Email: \href{mailto:}{masavirkhliq@iisc.ac.in}\\
		\href{https://www.musavirkhaliq.com}{Portfolio: www.musavirkhaliq.com} & Mobile:~~~+91-8825063816 \\
		\href{https://github.com/Musavirkhaliq}{Github: ~~github.com/MusavirKhaliq} \\
	\end{tabular*}
	
	%-----------EDUCATION-----------------
	\section{~~Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Indian Institute Of Science(IISc)}{Bangalore, India}
	{Masters of Technology - Computer Science and Automation;}{Aug 2021 - ongoing}
	{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Machine Learning for signal Processing, Computing fot AI and ML, Analysis Of Algorithms, Deep Learning for NLP, Game Theory, Computer architecture ,Graphics and Visualization, Cryptography , Distributed Computing Systems, Computational Topology }}}
	\resumeSubHeadingListEnd
	\resumeSubHeadingListStart
	\resumeSubheading
	{Punjab Technical University}{Bathinda Punjab, India}
	{Bachelor of Technology - Computer Science and Engineering;  GPA: 8.48}{Aug 2016 - July 2020}
	{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Compiler Design,Automata theory,Discerete Mathematics, Computer Networks, Databases}}}
	\resumeSubHeadingListEnd
	
	
	\vspace{-5pt}
	\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python,  C/C++,JAVA}
	\resumeSubItem{Packages}{~~~~~~~~NumPy,Matplotlib,Seaborn,Pandas,Scikit, NLTK, SpaCy,Pytorch, TensorFlow, Keras}
	\resumeSubItem{Databases}{~~~~~~MySQL}
	\resumeSubItem{Visualization}{~~Tableu[Filters, Data Visualization, Dashboards and Story
		Telling],Exploratory Data Analysis}
	\resumeSubItem{Machine Learning}{PCA, t-SNE, Linear/Logistic Regression, Decision Trees,
		Random Forest, KNN, SVM, NaiveBayes.}
	\resumeSubItem{Deep Learning}{MLP, CNN,LSTM,GANs,Encoder-Decoder Models,Attention Models,Transformers and BERT,Object detection}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking}
	
	\resumeSubHeadingListEnd
	\vspace{-5pt}
	\section{Experience}
	\resumeSubHeadingListStart
	\resumeSubheading{Mindtree}{}
	{AI Research Scientist  (Intern) Received Pre-Placement Offer}{May 2022 - Aug 2022}
	\resumeItemListStart
	\resumeItem{Adversarial Generation of Synthetic Tabular data}\\
	{-Found gaps in current research and proposed new techniques.}\\
	{-Implemented SOTA methods for Tabular data generation using GANs}\\
	{-Presented my work to MindTree's Research team }
	
	\resumeItemListEnd
	\vspace{-5pt}
	\resumeSubheading
	{Educasheer Ed-Tech Non-Profit Organisation}{}
	{Founder}{}
	\resumeItemListStart
	\resumeItem{About EduCasheer}
	{EduCasheer is a non-profit ED-Tech Startup. I handled technical as well as managerial side at EduCasheer.}
	\resumeItem{Purpose of EduCasheer}
	{The purpose of educasheer is to compensate education loss due to ongoing chaos in Kashmir Valley.\href{www.educasheer.com}{EduCasheer}}
	\resumeItem{Impact}{Courses we created include machine learning, computer programming. We have impacted a lot of students. }
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	%-----------PROJECTS-----------------
	\vspace{-5pt}
	\section{Projects}
	\resumeSubHeadingListStart
	\resumeSubItem{Privacy Preserving Recommendation Systems using Matrix Factorization\\Prof. Arpita Patra}  \null\hfill Jan 2023- June 2023
	\vspace{5pt}
	{\\
		- Dataset name : Movielens, Netflix \\
		- User-rating matrix was factorized by using ALS algorithm \\
		- ASTRA protocol was used to do the private computation\\
		}
		\resumeSubItem{Human Activity prediction \\
		{Applied Roots}} \null\hfill Sep. 2022
	\vspace{5pt}
	{\\
		- Human activity dataset from kaggle was used.\\
		- Different Models were trained and activity was predicted.
	}
	\resumeSubItem{Generating Synthetic Tabular Data using GANs\\Amit Modak, MindTree}  \null\hfill May 2022- July 2022
	\vspace{5pt}
	{\\
		- Tabular data was given with discrete and continuous columns\\
		-  Each row is treated as a joint distribution. \\
		- Data was cleaned and CTGANs were used to adversarially train the model.\\
		- Model output was synthetic data, which mimicked the actual distribution\\
	}

	\resumeSubItem{Classification of audio files using GMM \\
		{Prof. Sriram Ganapathy, Machine Learning for signal Processing}} \null\hfill Mar. 2022
	\vspace{5pt}
	{\\
	- Data-set contained Audio files which were either music or speech files.\\
	- Spectrogram features were generated using log magnitude with a 64 component magnitude FFT.\\
	- Two GMM models were trained with k-means initialization (for each class) separately each with \\
	(i) 2 mixtures with diagonal covariance, \\
	(ii) 2 mixtures with full covariance and\\
	(iii) 5-mixture components with diagonal/full covariance respectively on given data.\\
-Using this built classifier, classification of files was done. }
	\vspace{2pt}
	\resumeSubItem{Unsupervised Sentiment Analysis\\Prof. Sriram Ganapathy, Machine Learning for signal Processing}  \null\hfill Mar. 2022
	\vspace{5pt}
	{\\
	- Dataset name : movie review data (each line is an individual review).\\
	- Average TF-IDF featureas a document embedding vector was used.\\
	- PCA was used on embedding vector to reduce dimensionality to 10 dimensions.\\
	- Used 2GMM with diagonal covariance to identify label of the review.}
	\resumeSubItem{Facial Emotion Recognition in a live video\\Prof. Sriram Ganapathy, Machine Learning for signal Processing}  \null\hfill Apr. 2022
	\vspace{5pt}
	{\\
	- using CNN’s in a live video face expression was detected\\
	- Intensity of facial emotional was also computed}
	\resumeSubItem{Optimizing performance of Checkered Matrix Multiplication \\ Prof. Arka Prava Basu, Computer architecture}  \null\hfill Sep. 2021
	\vspace{5pt}
	{\\
		- Perf analysis was done to find performance bottlenecks.\\
		- CMM was optimized by using cache locality.\\
		- parallelism was achieved on GPU using CUDA\\}
	\resumeSubHeadingListEnd
	\vspace{-5pt}
	
	%-----------Awards-----------------
	\section{Achievementss and Awards}
	\begin{description}[font=$\bullet$]
		\item \textbf{Reliance Foundation Scholarship for Academic Excellence for the year 2021-22 }\\
		The Reliance Foundation Scholarships is a merit-based scholarship enabling India's brightest youth to become the leaders of tomorrow for social good. 40 postgraduate students nationwide are awarded this scholarship.
		\vspace{-5pt}
		\item \textbf{Amazon Summer School - July, 2022 }\\
		Bunch of students are selected by amazon for the ML program. The program gives engineering students in India an opportunity to learn machine learning techniques from tenured scientists at Amazon.  
		\vspace{-5pt}
		\item \textbf{Student ambassador in EECS-Division for GATE-JAM -SEP, 2022 }\\
		The EECS divison of IISc chose six students to address the nation's prospective research applicants. We visit universities of our nation to interact with students.
		\vspace{-5pt}
		\item \textbf{Founded Databased @ IISc - Nov 2022}\\
		It is a community of students passionate about diving deep into the world of computer science, ML and DL. Along with leading the club I also teach Applied Machine Learning and Deep Learning to the community.
		\vspace{-5pt}

		
	\end{description}
	
	\vspace{-5pt}
	\section{Volunteer Experience}
	\resumeSubHeadingListStart
	\resumeSubheading
	{CSA OpenDay Core team member}{IISc Bangalore, India}
	{Organized the whole OpenDay Event for CSA }{Mar 2023}
	\vspace{5pt}
	\resumeSubheading
	{Student Representative of CSA}{IISc Bangalore, India}
	{Dealt with student onboarding and taught some courses along with other people. }{July 2022 - Present}
	\vspace{5pt}
	% \vspace{10pt}\textbf{\large{Community Experience}}
	\resumeSubheading
	{Student Lead of Builders Club}{IISc Bangalore, India}
	{Here we conduct coding contests every saturday. Discuss ideas interact with industry leaders.}{Aug 2022 - Present}
	% \vspace{10pt}\textbf{\large{Community Experience}}
	\resumeSubheading
	{Placement Coordinator of CSA}{IISc Bangalore, India}
	{Get in touch with companies}{Aug 2022 - Present}
	
	
	\resumeSubHeadingListEnd
	
\end{document}